log

### 2020-05-14 datasets/readme.Rmd
readme update

## software dataset
```{r}
hall <- template

@@

# Statistics
All candidate papers, paper selected for full text screening, papers included in final review and inclusion rate, over various versions of the dataset.  
```{r, echo = FALSE}
tibble(Dataset = names(all), 
       # paper 
       `candidates_paper` = nostudies(all, "paper", "search"), 
       `fulltext_paper` = nostudies(all, "paper", "ftext"),
       `incl_paper` = nostudies(all, "paper", "incl"),
       `inclrate_paper` = inclrate(all, "paper"),

       # raw data 
       `candidates_raw` = nostudies(all, "raw", "search"), 
       `fulltext_raw` = nostudies(all, "raw", "ftext"),
       `incl_raw` = nostudies(all, "raw", "incl"),
       `inclrate_raw` = inclrate(all, "raw"),

       # asreview repository 
       `candidates_asr` = nostudies(all, "asreview", "search"), 
       `fulltext_asr` = nostudies(all, "asreview", "ftext"),
       `incl_asr` = nostudies(all, "asreview", "incl"),
       `inclrate_asr` = inclrate(all, "asreview"),

       # test set 
       `candidates_test` =  nostudies(all, "test", "search"), 
       `fulltext_test` =  nostudies(all, "test", "ftext"), 
       `incl_test` =  nostudies(all, "test", "incl"), 
       `inclrate_test` = inclrate(all, "test")) %>% 
  t() %>% 
  kable("markdown", digits = 2) 
# %>%
#   kable_styling(full_width = TRUE) %>%
#   #scroll_box(width = "100%", height = "200px") %>%
#   pack_rows("Paper", 2, 5) %>%
#   pack_rows("Raw data", 6, 9) %>%
#   pack_rows("ASReview data", 10, 13) %>%
#   pack_rows("Test data set", 14, 17)  
```

Descriptives on missingness and duplicate abstracts in the ASReview test data set. 
```{r, echo = FALSE}
drops %>%
  kable("markdown",
        col.names = c("n", "NA", "NA rate (%)", "duplicates", "duplicate rate (%)"),
        digits = 2)

@@

To check:
```{bash , eval = FALSE}
asreview stat test_datasets/*
```

returns 
```
************  ace.csv  ************

Number of papers:            2235
Number of inclusions:        41 (1.83%)
Number of exclusions:        2194 (98.17%)
Number of unlabeled:         0 (0.00%)
Average title length:        123
Average abstract length:     1623
Average number of keywords:  15.0
Number of missing titles:    0 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)

************  nudging.csv  ************

Number of papers:            1847
Number of inclusions:        100 (5.41%)
Number of exclusions:        1747 (94.59%)
Number of unlabeled:         0 (0.00%)
Average title length:        109
Average abstract length:     1831
Average number of keywords:  None
Number of missing titles:    0 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)

************  ptsd.csv  ************

Number of papers:            5031
Number of inclusions:        38 (0.76%)
Number of exclusions:        4993 (99.24%)
Number of unlabeled:         0 (0.00%)
Average title length:        104
Average abstract length:     1537
Average number of keywords:  9.9
Number of missing titles:    1 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)

************  software.csv  ************

Number of papers:            8896
Number of inclusions:        104 (1.17%)
Number of exclusions:        8792 (98.83%)
Number of unlabeled:         0 (0.00%)
Average title length:        81
Average abstract length:     896
Average number of keywords:  None
Number of missing titles:    0 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)

************  virus.csv  ************

Number of papers:            2304
Number of inclusions:        114 (4.95%)
Number of exclusions:        2190 (95.05%)
Number of unlabeled:         0 (0.00%)
Average title length:        103
Average abstract length:     1345
Average number of keywords:  20.3
Number of missing titles:    0 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)

************  wilson.csv  ************

Number of papers:            2333
Number of inclusions:        23 (0.99%)
Number of exclusions:        2310 (99.01%)
Number of unlabeled:         0 (0.00%)
Average title length:        83
Average abstract length:     1325
Average number of keywords:  31.3
Number of missing titles:    1 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)

```
# refrences

>>>>

## Software dataset
```{r}
hall <- template

@@

# Statistics
All candidate papers, paper selected for full text screening, papers included in final review and inclusion rate, for the test datasets. 
```{r, echo = FALSE, eval = TRUE, warning = FALSE}
tibble(Dataset = names(all), 
       # paper 
       # `candidates_paper` = nostudies(all, "paper", "search"), 
       # `fulltext_paper` = nostudies(all, "paper", "ftext"),
       # `incl_paper` = nostudies(all, "paper", "incl"),
       # `inclrate_paper` = inclrate(all, "paper"),
       # 
       # # raw data 
       # `candidates_raw` = nostudies(all, "raw", "search"), 
       # `fulltext_raw` = nostudies(all, "raw", "ftext"),
       # `incl_raw` = nostudies(all, "raw", "incl"),
       # `inclrate_raw` = inclrate(all, "raw"),
       # 
       # # asreview repository 
       # `candidates_asr` = nostudies(all, "asreview", "search"), 
       # `fulltext_asr` = nostudies(all, "asreview", "ftext"),
       # `incl_asr` = nostudies(all, "asreview", "incl"),
       # `inclrate_asr` = inclrate(all, "asreview"),
       # 
       # test set 
       `candidates_test` =  nostudies(all, "test", "search"), 
       `fulltext_test` =  nostudies(all, "test", "ftext"), 
       `incl_test` =  nostudies(all, "test", "incl"), 
       `inclrate_test` = inclrate(all, "test")) %>% 
  t() %>% 
  kable("markdown", digits = 2) 
# %>%
#   kable_styling(full_width = TRUE) %>%
#   #scroll_box(width = "100%", height = "200px") %>%
#   pack_rows("Paper", 2, 5) %>%
#   pack_rows("Raw data", 6, 9) %>%
#   pack_rows("ASReview data", 10, 13) %>%
#   pack_rows("Test data set", 14, 17)  
```

Descriptives on missingness and duplicate abstracts in the raw datasets: 
```{r, echo = FALSE}
drops %>%
  kable("markdown",
        col.names = c("n", "NA", "NA rate (%)", "duplicates", "duplicate rate (%)"),
        digits = 2)

@@

# References

### 2020-05-14 results/README.Rmd
readme update

- `extract_plots.ipynb`, a jupyter notebook producing recall curves from the simulation output (Figure 1 and 2 in the manuscript)
- `extract_results.ipynb`, a jupyter notebook extracting `.json` files containing statistics from the simulation output (WSS, RRF, ATD in table 2, 3, and 4 in the manuscript)
- `one_seed`, containing all plots and data produced by the two jupyter notebooks above.
- `README.Rmd` containing R-code to transform the .json files into readable tables for the manuscript.
- `output` contains the abovementioned tables, stored as .RDS files.

>>>>

- `extract_plots.ipynb`, a jupyter notebook producing recall curves from the simulation output (Figure 1 and 2 in the manuscript)
- `extract_results.ipynb`, a jupyter notebook extracting `.json` files containing statistics from the `.h5` simulation output (WSS, RRF, ATD in table 2, 3, and 4 in the manuscript)
- `one_seed`, containing all plots and data produced by the two jupyter notebooks above.
- `README.Rmd` containing R-code to transform the .json files into readable tables for the manuscript.
- `output` contains the abovementioned tables, stored as .RDS files.

# Requirements
Extracing data from the simulation output requires having several packages installed, like ASReview version 0.9.3 [@ASReview2020]. All these requirements are listed in the `requirements.txt` file. If you've already installed this file in the `simulation_study` step, please skip this. If not, you can run the following in your terminal to install all requirements: 
```{bash, eval = FALSE}
pip install -r ../simulation_study/requirements.txt
```

Additionally, to create the plots and statistics in the manuscript you will need to install a specific branch of the asreview visualization package. Run the following in your terminal: 
```{bash, eval = FALSE}
# clone visualization package from GitHub
git clone https://github.com/GerbrichFerdinands/asreview-thesis-visualization.git
```

And then, within the newly created directory, the following:

```{bash, eval = FALSE}
# install visualization package 
pip install . 
```

### 2020-05-14 simulation_study/README.Rmd
readme update

---
title: "log"
output:   
  md_document:
    variant: markdown_github
---

The log of the simulation study.

- hpoptimization. 
  - Sripts for hyperparameter optimization
  - 
- simulation 
  - scripts for simulation studies

@@

```{r, eval = FALSE}
# 
source("R/00_condition_grid.R")
source("R/01_hyperparameter_sets.R")
```

## Hyperparameter optimization
There are three stages, we start with the first 5 where we are comparing different classifiers.

```{r}
conditiongrid <- readRDS("R/00_conditiongrid.RDS")
conditiongrid %>%
  kable(format = "markdown")
```

### Version information
Personal device: macos catalina 10.15.2

Cartesius supercomputer 
asreview 0.7.2
asreview simulation branch reorganization.

-----

# Stage 1 - Classifiers 
Comparing five different classifiers
```{r}
emptytodo <- readRDS("R/01_hyperparameter_sets.RDS")
todo <- emptytodo
```

R - 275 secs 119% - 5 datasets 
```{r}
275 / 5 * 1000 / 60 # 916 minutes
```

## 1.1 Optimizing (hyper)parameters per model, per dataset (1-1)
```{r}
lubridate::date("2020-03-17")
# i am working on svm model for all datasets 
todo <- busy(todo, "SCTW", "one", "ace")
```

Optimization run on Cartesius
```{bash, eval = FALSE}
# BCTW
# RCTW
# SCTW 
./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d ace -r 23 # job id 7768402
# LCTW
# NCTW
```

***

```{r}
lubridate::date("2020-03-18")
todo <- check(todo, "BCTW", "one", datasets)
todo <- check(todo, "SCTW", "one", "ace")
```

Store config files from job 7768402, SCTW model.

```{bash, eval = FALSE}
asreview create-config output/active/svm_max_double_tfidf/ace/trials.pkl -o config/SCTW_ace.ini
```

Transfer config files to my computer home directory 
```{bash, eval = FALSE}
# in own device. 
scp gerbrich@cartesius.surfsara.nl:asreview/config/SCTW_ace.ini ~
```

```{bash, eval = FALSE}
# BCTW
./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d ace -r 23 # 7772446
./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d nudging -r 23 # 7772450
./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d ptsd -r 23 # 7772452
./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d software -r 23 # 7772454
./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d wilson -r 23 # 7772456
# extract all trials.pkl files 
scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/ace/trials.pkl ~/hyperopt/trials/BCTW_ace.pkl 
scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/nudging/trials.pkl ~/hyperopt/trials/BCTW_nudging.pkl 
scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/ptsd/trials.pkl ~/hyperopt/trials/BCTW_ptsd.pkl
scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/software/trials.pkl ~/hyperopt/trials/BCTW_software.pkl 
scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/wilson/trials.pkl ~/hyperopt/trials/BCTW_wilson.pkl 
# create config files
asreview create-config trials/BCTW_ace.pkl -o config/BCTW_ace.ini
asreview create-config trials/BCTW_nudging.pkl -o config/BCTW_nudging.ini
asreview create-config trials/BCTW_ptsd.pkl -o config/BCTW_ptsd.ini
asreview create-config trials/BCTW_software.pkl -o config/BCTW_software.ini
asreview create-config trials/BCTW_wilson.pkl -o config/BCTW_wilson.ini
# RCTW
# SCTW 
# LCTW
# NCTW
```

***

```{r}
lubridate::date("2020-03-19")
#todo <- check(todo, "BCTW", "one", datasets)
```

### simulations with nb 
```{bash, eval = FALSE}
# create config files within cartesius (scripts folder)
asreview create-config output/active/nb_max_double_tfidf/ace/trials.pkl -o config/BCTW_ace.ini
asreview create-config output/active/nb_max_double_tfidf/nudging/trials.pkl  -o config/BCTW_nudging.ini
asreview create-config output/active/nb_max_double_tfidf/ptsd/trials.pkl  -o config/BCTW_ptsd.ini
asreview create-config output/active/nb_max_double_tfidf/software/trials.pkl  -o config/BCTW_software.ini
asreview create-config output/active/nb_max_double_tfidf/wilson/trials.pkl  -o config/BCTW_wilson.ini
```

```{bash, eval = FALSE}
# run simulations within cartesius
./cart_simulate.py data/ace.csv --config_file config/BCTW_ace.ini --state_file "simoutput/bctw/ace/BCTW_ace.h5" -r 23 
./cart_simulate.py data/nudging.csv --config_file config/BCTW_nudging.ini --state_file "simoutput/bctw/nudging/BCTW_nudging.h5" -r 23 
./cart_simulate.py data/ptsd.csv --config_file config/BCTW_ptsd.ini --state_file "simoutput/bctw/ptsd/BCTW_ptsd.h5" -r 23 
./cart_simulate.py data/software.csv --config_file config/BCTW_software.ini --state_file "simoutput/bctw/software/BCTW_software.h5" -r 23 
./cart_simulate.py data/wilson.csv --config_file config/BCTW_wilson.ini --state_file "simoutput/bctw/wilson/BCTW_wilson.h5" -r 23 
```

### extract simulation results nb 
```{bash, eval = FALSE}
# transfer files to device 
scp -r gerbrich@cartesius.surfsara.nl:asreview/simoutput /Users/gerbrich/Documents/MSBBSS/asreviewthesis/asreview-thesis/simulation_output
scp -r /Users/gerbrich/Documents/MSBBSS/asreviewthesis/asreview-thesis/hyperopt/config/one gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config
```

```{bash, eval = FALSE}
# on own device
asreview plot asreview-thesis/simulation_output
```

***
```{r}
lubridate::date("2020-03-22")
todo <- busy(todo, "SCTW", "one", datasets[2:5])
todo <- busy(todo, c("LCTW", "RCTW", "NCDW"), "one", "ace")
todo <- not(todo, "NCTW", "one", datasets)
# do the remaining datasets of svm, and one test run for L and one for R. 
```

Sent hyperparameters for optimization
```{bash, eval = FALSE}
# SCTW
./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d nudging -r 23 # 7805983
./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d ptsd -r 23 # 7805984
./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d software -r 23 # 7805985
./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d wilson -r 23 # 7805986
# LCTW 
./cart_hyper_run.py hyper-active -t 12:00:00 -m lr -b double -e tfidf -q max -d ace -r 23 # 7805987
# RCTW 
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7805989
# NCTW does not work well with tfidf, save for second round with doc2vec: 
# NCDW
./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 23 # 7806021
```

***
```{r}
lubridate::date("2020-03-23")
todo <- check(todo, "SCTW", "one", datasets[3:5])
```

Checkout hyperopt SCTW
Nudging dataset doesn't optimize well? 
```{r}
todo <- huh(todo, "SCTW", "one", "nudging")
todo <- check(todo, "SCTW", "one", "nudging")
```

### Checkout results first hyperopt 
LCTW - no output? 
RCTW - only 'current'
```{r}
todo <- huh(todo, c("LCTW", "RCTW"), "one", "ace")
```

```{bash, eval = FALSE}
# LCTW 
# made a mistake in command, "logistic" instead of "lr", run again 
./cart_hyper_run.py hyper-active -t 03:00:00 -m logistic -b double -e tfidf -q max -d ace -r 23 # 7813556
# evaluated run, now other datasets
./cart_hyper_run.py hyper-active -t 09:00:00 -m logistic -b double -e tfidf -q max -d ace -r 23 # 7815137
./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d nudging -r 23 # 7815154
./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d ptsd -r 23 # 7815155
./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d software -r 23 # 7815156
./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d wilson -r 23 # 7815157
# RCTW, fixed a parameter bug in simulation package. 
./cart_hyper_run.py hyper-active -t 03:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7813592
# evaluated run, now other datasets
./cart_hyper_run.py hyper-active -t 09:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7815139
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d nudging -r 23 # 7815158
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d ptsd -r 23 # 7815159
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d software -r 23 # 7815160
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d wilson -r 23 # 7815162
```

```{r}
todo <- busy(todo, c("LCTW", "RCTW"), "one", datasets)
```

NCDW - loss still going down, sent in for another 12 hours. 
```{bash, eval = FALSE}
# NCDW
./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 23 # 7811926
# error 
# accidentally got killed while downgrading tensorflow at the same time. 
# run again, 7815147
# NCDW for remaining datasets 
```

Resimulate BCTW models.
 - create-config file from trials.pkl: n_instances 20, 1/1
 - how to overrule this parameters? (not possible through cli)

```{bash, eval = FALSE}
./cart_simulate.py data/ace.csv --config_file config/one/BCTW_ace.ini --state_file "simoutput/bctw/ace/results_ace.h5" -r 23 # 7814382
./cart_simulate.py data/nudging.csv --config_file config/one/BCTW_nudging.ini --state_file "simoutput/bctw/nudging/results_nudging.h5" -r 23 # 7814384
./cart_simulate.py data/ptsd.csv --config_file config/one/BCTW_ptsd.ini --state_file "simoutput/bctw/ptsd/results_ptsd.h5" -r 23 # 7814391
./cart_simulate.py data/software.csv --config_file config/one/BCTW_software.ini --state_file "simoutput/bctw/software/results_software.h5" -r 23 # 7814392 
./cart_simulate.py data/wilson.csv --config_file config/one/BCTW_wilson.ini --state_file "simoutput/bctw/wilson/results_wilson.h5" -r 23 # 7814395
```

Optimize BCTW model 6 datasets (for paper)
```{bash, eval = FALSE}
./cart_hyper_run.py hyper-active -t 5 -b triple -r 23 # 7815097
./cart_hyper_run.py hyper-active -t 12:00:00 -b triple -r 23 # 7815102
# create config file (BMTW (M=mixed)) 
asreview create-config output/active/nb_max_random_triple_tfidf/ptsd_virus_ace_software_wilson_nudging/trials.pkl -o config/BMTW_all.ini
# move config to device
scp gerbrich@cartesius.surfsara.nl:asreview/config/BMTW_all.ini ~/
# run simulations (on own device)
# see script
```

***

```{r}
lubridate::date("2020-03-27")
# todo <- busy(todo, "SCTW", "one", datasets[2:5])
```

Process BCTW models simulations into table
 - python script to extract statistics

Create checklist table for simulations

Checkout what happened with NCDW and other errors in hpcbatch 
```{bash, eval = FALSE}
# retest with hall dataset 
./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d hall -r 23 # 7843185
```

Simulate SCTW models

Process SCTW models into table

Simulate LCTW, RCTW and NCTW models 
   - create config files
   - run simulation

Create a nice plot

Send first version of table

Move all hyperopt results to harddrive

scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/output/active /Volumes/Gerbrich/asreview/archive/output

scp -r gerbrich@cartesius.surfsara.nl:/output/active/nb_max_random_triple_tfidf ~

scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/output/active/nb_max_random_triple_tfidf ~

scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/output/active/nb_max_random_triple_tfidf/ptsd_virus_ace_software_wilson_nudging/best ~
***

```{r}
# save the to-do grid in markdown style
todo[todo==0] <- emo::ji("white square button")
todo %>% kable(format = "markdown")
saveRDS(todo %>% kable(format = "markdown"), 
        file = "02_todo_hp.RDS")
```

## Stage 2 - Feature extraction 
Comparing tfidf with doc2vec

## Stage 3 - Balance strategy
Redo all the analyses with a different balance strategy (aggressive undersampling?)
Probably won't have time for this.

# The data 
On 17 march 2020:

```
************  ace.csv  ************
Number of papers:            2235
Number of inclusions:        41 (1.83%)
Number of exclusions:        2194 (98.17%)
Number of unlabeled:         0 (0.00%)
Average title length:        123
Average abstract length:     1623
Number of missing titles:    0 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)
************  nudging.csv  ************
Number of papers:            1847
Number of inclusions:        100 (5.41%)
Number of exclusions:        1747 (94.59%)
Number of unlabeled:         0 (0.00%)
Average title length:        109
Average abstract length:     1831
Number of missing titles:    0 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)
************  ptsd.csv  ************
Number of papers:            5031
Number of inclusions:        38 (0.76%)
Number of exclusions:        4993 (99.24%)
Number of unlabeled:         0 (0.00%)
Average title length:        104
Average abstract length:     1537
Number of missing titles:    1 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)
************  software.csv  ************
Number of papers:            8896
Number of inclusions:        104 (1.17%)
Number of exclusions:        8792 (98.83%)
Number of unlabeled:         0 (0.00%)
Average title length:        81
Average abstract length:     896
Number of missing titles:    0 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)
************  wilson.csv  ************
Number of papers:            2333
Number of inclusions:        23 (0.99%)
Number of exclusions:        2310 (99.01%)
Number of unlabeled:         0 (0.00%)
Average title length:        83
Average abstract length:     1325
Number of missing titles:    1 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)
```

>>>>

---
title: "log"
output:   
  md_document:
    variant: markdown_github
bibliography: ../manuscript/manuscript/asreview.bib
---

This directory contains all steps taken in hyperparameter optimization and simulating automated systematic reviews.

@@

# Models 
We are simulating 7 models on 6 systematic review datasets. Each model has an abbreviation to ease the programming process: 
```{r, eval = FALSE}
#  
# source("R/00_condition_grid.R")
# source("R/01_hyperparameter_sets.R")

conditiongrid <- readRDS("R/00_conditiongrid.RDS")

conditiongrid[c(1:4, 7:9),] %>%
  mutate(Model = c("NB + TF-IDF", "LR + D2V", "LR + TF-IDF", "RF + D2V", "RF + TF-IDF", "SVM + D2V", "SVM + TF-IDF" )) %>%
  mutate(Abbreviation = condition) %>%
  select(Model, Abbreviation)
  kable(format = "markdown")
```
The first letter denotes the classification strategy, NB, LR, RF, or SVM. The second letter stands for C of certainty sampling. The third letter denotes the feature extraction strategy, TF-IDF or Doc2vec. The fourth letter stands for D of Dynamic Resampling.

# Requirements 
This study requires having several packages installed, like ASReview version 0.9.3 [@ASReview2020]. 
All these requirements are listed in the `requirements.txt` file. Assuming you have Python 3.7 or higher, you can run the following to install all requirements: 
```{bash, eval = FALSE}
pip install -r requirements.txt
```

### Version information
Personal device: macos catalina 10.15.2
Cartesius supercomputer 
asreview simulation branch reorganization.

# References
